### 2020-03-16 writeup/setup.tex
wip

In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
We use a shared body (module) $B$ for all tasks and a separate head (module) $\set{A_i}_{i=1}^k$ for each task.
%    \paragraph{Different covariates:}
This corresponds to minimizing the following optimization objective.
\begin{align}
	\label{eq_mtl}
	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \norm{X_i B A_i - Y_i}^2.
\end{align}
Note that we consider the natural parameterization without reweighting the tasks above.
The shared body $B$ plays an important role because it allows information transfer between different task data.

>>>>

In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{A_i}_{i=1}^k$ for each task.
%    \paragraph{Different covariates:}
This corresponds to minimizing the following optimization objective.
\begin{align}
	\label{eq_mtl}
	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \norm{X_i B A_i - Y_i}^2.
\end{align}
Note that we consider the natural parameterization without reweighting the tasks above.
The shared body $B$ plays an important role because it allows information transfer between different task data.
There are two ways to ensure the sharing of information between tasks.
\begin{itemize}
	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
	\item Controlling the capacity $r$ of $B$.
\end{itemize}
